In this work we have explored the impact of several limitations in physical
reservoir computing (RC). Through Echo State Network (ESN) simulations we have
uncovered characteristics exhibited by white noise, quantization noise and
partially visible reservoirs in prediction of the NARMA10 time series.

By modeling additive white Gaussian noise (AWGN) we have found that the RC
paradigm provides an inherent robustness to noisy inputs. This is a promising
result when considering physical substrates as a reservoir medium, suggesting a
lower bound of 10dB on the ratio of signal power to noise power that is
tolerable to provide a satisfactory representation of the signal in the
reservoir dynamics.

Moreover, our experiments show that this resilience to white noise also extends
to ADC quantization noise. By quantizing the output of the $\tanh$ activation
function of hidden nodes in the ESNs, we have demonstrated that general
reconstruction capability of our reservoirs on the NARMA10 task is unhindered
when using an ADC with 12 bits of resolution or more.

We have also investigated the importance of input and output connectivity, as to
provide insights into reservoirs that are only partially visible to an
observer.

We found the optimal input connectivity to be when 10\% to 20\% of the reservoir
nodes see the input stream, and that the distribution of the input weights of
the ESNs is of little relevance to performance, which introduces flexibility in
the choice of reservoir perturbation.

No clear performance difference was found across reservoirs of varying sizes
when the amount of connected output nodes remains the same. This illustrates the
importance both of having a sufficient amount of output nodes, and that the
physical layout of these nodes should be such that enough of the reservoir
dynamics is captured.

The work presented contains an introductory exploration of physical limitations
in RC, and thus casts quite a wide net. Developing a concrete understanding of
the issues faced when moving simulation models to physical realizations is a
prerequisite to exploiting computational properties in matter. With ESN
simulations we have demonstrated the particular impact of several common
physical limits, which should be transferable to reservoirs manifesting similar
dynamics.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
